\section{Problem Statement / Limitations}

Practical laboratory examinations are often conducted in environments where the technical challenge of the assessment is matched by an equally serious management challenge. In many institutions, there is no single platform that coordinates scheduling, invigilation, access control, workstation-level tracking, incident recording, and post-exam reporting in a unified way \cite{pmc_cbt}. As a result, important parts of the process remain manual, fragmented, or weakly documented. This makes the examination workflow harder to supervise and more difficult to justify when concerns arise.

One of the most significant limitations of the current environment is the limited ability of invigilators to monitor many students simultaneously with confidence \cite{mit_cbt}. In a crowded computer lab, human attention alone is often insufficient to maintain real-time awareness of who has started, who is inactive, who may be experiencing technical issues, and who may be deviating from expected behavior. Even when invigilators are experienced, the lack of a consolidated dashboard makes consistent situational awareness difficult.

A second limitation concerns evidence and traceability \cite{integ1}. In many practical exams, suspicious activity, submission problems, or timing disputes are difficult to reconstruct after the session has ended. Without structured logs and organized incident records, academic decisions may depend on fragmented observations rather than well-preserved evidence. A third limitation lies in the administrative workload caused by separate tools and manual coordination. Scheduling, attendance, monitoring, submission collection, and reporting may each require different artifacts or systems, increasing operational overhead and the possibility of inconsistency.

The proposed project itself also has development limitations. As an FYP, it will emphasize a well-structured prototype and academically defensible design rather than claiming full enterprise-scale deployment across all university departments. Advanced AI-driven anomaly detection may initially be represented through configurable monitoring logic and alert support rather than through a production-trained predictive model. Similarly, large-scale live deployment constraints such as network variability, institutional integration complexity, and long-term maintenance policies may remain outside the immediate prototype boundary. These limitations are acknowledged so that the project remains realistic while still delivering meaningful academic and operational value.
