\section{Benefits of Proposed System}

The proposed system offers a set of integrated capabilities that directly address the operational difficulties of practical laboratory examinations. Role-based user management supports different workflows for administrators, teachers, invigilators, and students, which helps the institution align permissions with responsibilities and reduce unauthorized access to sensitive exam functions \cite{rbac1}.

Exam creation and scheduling allow authorized academic staff to define practical exams, assign dates and durations, publish instructions, and map sessions to relevant users and labs \cite{eassess1}. This improves planning consistency and reduces confusion before the session begins.

Lab and workstation control strengthens the connection between the digital workflow and the physical laboratory environment by associating sessions with approved machines and locations. This is especially important in practical exams, where the technical workspace matters as much as the question paper itself \cite{pmc_cbt}.

Secure exam execution gives students a controlled and time-bound environment that is aligned with the scheduled session. This reduces ambiguity in exam start and finish conditions and supports procedural fairness \cite{integ1}.

The live monitoring dashboard gives invigilators a centralized view of active students, session status, timing, and alerts \cite{mit_cbt}. This directly addresses the supervision challenges that emerge when many students are simultaneously working in the lab.

Alerting and evidence logging preserve meaningful exam events and suspicious occurrences as structured evidence \cite{integ1}. This improves post-exam review and strengthens accountability.

Submission management organizes student work through a controlled workflow that links each file or output with the correct candidate and session \cite{eassess1}. This reduces the risk of disorganized file collection and supports cleaner evaluation.

Instructor review and administrative reporting help departments review attendance, incidents, session histories, and submission records through consolidated reporting features. This improves institutional documentation and helps departments learn from each conducted session \cite{spp1}.

The proposed solution is therefore not simply a secure browser, not simply a submission portal, and not simply an academic reporting tool. It is an integrated environment deliberately tailored to the needs of practical laboratory examinations. By addressing planning, supervision, traceability, and reporting in one coherent platform, it aims to produce a system that is academically useful, operationally realistic, and institutionally defensible \cite{sommerville}.

