\begin{thebibliography}{99}

%% Entries ordered by first appearance in document: Ch1-1 -> Ch3-6

%% [1] Ch1-1 para1
\bibitem{pmc_cbt} NCBI, ``Computer-based testing in higher education,'' Available: \url{https://pmc.ncbi.nlm.nih.gov/articles/PMC12874087/}

%% [2] Ch1-1 para2
\bibitem{mit_cbt} MIT Open Learning, ``Computer-based testing: secure, efficient, cost-effective,'' Available: \url{https://openlearning.mit.edu/mit-faculty/residential-digital-innovations/computer-based-testing-secure-efficient-cost-effective}

%% [3] Ch1-1 para2 (end)
\bibitem{integ1} IEEE, ``Academic Integrity and Technology,'' Available: \url{https://www.ieee.org/education/resources.html}

%% [4] Ch1-2 Product Scope
\bibitem{scope1} PMI, ``What is Project Scope?,'' Available: \url{https://www.pmi.org/learning/library/project-scope-management-essentials-8164}

%% [5]-[14] Ch1-2 Literature Review (applications in order of appearance)
\bibitem{respondus1} Respondus, ``LockDown Browser,'' Available: \url{https://web.respondus.com/he/lockdownbrowser/}

\bibitem{seb1} Safe Exam Browser, ``About Safe Exam Browser,'' Available: \url{https://safeexambrowser.org/about_overview_en.html}

\bibitem{moss1} Stanford University, ``MOSS: A System for Detecting Software Similarities,'' Available: \url{https://theory.stanford.edu/~aiken/moss/}

\bibitem{examsoft1} ExamSoft, ``Learning Assessment Tools \& Software,'' Available: \url{https://examsoft.com/}

\bibitem{moodle1} Moodle, ``Moodle and Assessment,'' Available: \url{https://moodle.com/moodle-and-assessment/}

\bibitem{proctorio1} Proctorio, ``The Learning Integrity Platform,'' Available: \url{https://proctorio.com/}

\bibitem{honorlock1} Honorlock, ``What is Online Proctoring? Types, Features, and Integrations,'' Available: \url{https://honorlock.com/blog/what-is-proctored-testing/}

\bibitem{blackboard1} Anthology, ``Blackboard Learn,'' Available: \url{https://www.anthology.com/products/teaching-and-learning/learning-effectiveness/blackboard/blackboard-learn}

\bibitem{canvas1} Instructure, ``Canvas LMS,'' Available: \url{https://www.instructure.com/canvas}

\bibitem{gclassroom1} Google for Education, ``Google Classroom,'' Available: \url{https://edu.google.com/workspace-for-education/classroom/}

%% [15] Ch1-3 Objectives
\bibitem{rbac1} NIST, ``Role-Based Access Control,'' Available: \url{https://csrc.nist.gov/projects/role-based-access-control}

%% [16] Ch1-5 Benefits
\bibitem{eassess1} R. Conole and M. Warburton, ``A review of computer-assisted assessment,'' \textit{Research in Learning Technology}, vol. 13, no. 1, pp. 17--31, 2005.

%% [17] Ch1-5 Benefits
\bibitem{spp1} PMI, \textit{A Guide to the Project Management Body of Knowledge (PMBOK Guide)}, 7th ed. Project Management Institute, 2021.

%% [18] Ch1-5 Benefits
\bibitem{sommerville} I. Sommerville, \textit{Software Engineering}, 10th ed. Pearson, 2015.

%% [19] Ch1-7 Intended Users (Student subsection)
\bibitem{biometric1} A. Jain, A. Ross, and S. Prabhakar, ``An introduction to biometric recognition,'' \textit{IEEE Transactions on Circuits and Systems for Video Technology}, vol. 14, no. 1, pp. 4--20, 2004.

%% [20] Ch2-1 SRS Introduction
\bibitem{srs1} IEEE Std 830-1998, \textit{IEEE Recommended Practice for Software Requirements Specifications}. IEEE, 1998.

%% [21] Ch2-2 Non-Functional Requirements
\bibitem{iso25010} ISO/IEC 25010:2011, \textit{Systems and software Quality Requirements and Evaluation (SQuaRE) -- System and software quality models}. International Organization for Standardization, 2011.

%% [22] Ch2-2 Requirement Gathering
\bibitem{elicit1} K. Pohl, \textit{Requirements Engineering: Fundamentals, Principles, and Techniques}. Springer, 2010.

%% [23] Ch3-1 Project Plan
\bibitem{agile1} Atlassian, ``What is Agile?,'' Available: \url{https://www.atlassian.com/agile}

%% [24] Ch3-2 Deliverables
\bibitem{del1} Atlassian, ``Project Deliverables,'' Available: \url{https://www.atlassian.com/work-management/project-management/project-deliverables}

%% [25] Ch3-3 Gantt Chart
\bibitem{gantt1} TeamGantt, ``What is a Gantt Chart?,'' Available: \url{https://www.teamgantt.com/what-is-a-gantt-chart}

%% [26] Ch3-3 WBS
\bibitem{wbs1} PMI, ``Work Breakdown Structure,'' Available: \url{https://www.pmi.org/learning/library/applying-work-breakdown-structure-project-lifecycle-6979}

%% [27] Ch3-3 Schedule Control
\bibitem{scrum1} Atlassian, ``What is Scrum?,'' Available: \url{https://www.atlassian.com/agile/scrum}

%% [28] Ch3-6 Risk Management
\bibitem{risk1} ISO 31000:2018, \textit{Risk Management -- Guidelines}. International Organization for Standardization, 2018.

%% [29] Ch3-6 Risk Identification
\bibitem{facerec1} NIST, ``Face Recognition Technology Evaluation (FRTE),'' Available: \url{https://www.nist.gov/programs-projects/face-recognition-vendor-test-frvt-ongoing}

\end{thebibliography}
