\newpage
\thispagestyle{empty}
\chapter*{\centering Project Overview}
\addcontentsline{toc}{chapter}{Project Overview}
The proposed project, AI-Driven Lab Exam Monitoring and Management System, addresses the need for a controlled and well-managed environment for practical laboratory examinations conducted in universities and other academic institutions. In courses such as programming, databases, software engineering, networking, and operating systems, students are assessed on institutional machines where academic integrity depends on secure access, proper scheduling, controlled workstation usage, continuous monitoring, organized submission handling, and dependable reporting. Existing tools usually address only one part of this process, such as browser lockdown, online quiz delivery, plagiarism detection, or grading support, but they do not provide one integrated workflow specifically designed for in-person lab examinations.

The scope of the project is to develop a unified academic platform that supports exam scheduling, user and role management, lab allocation, student authentication, face recognition support, AI-assisted monitoring, evidence logging, submission collection, result management, and report generation. The system is intended to reduce manual invigilation burden, improve institutional visibility during live exams, and maintain a stronger evidence trail for post-exam review. By combining these functions in one platform, the project aims to improve fairness, consistency, and accountability in practical assessments.

The development approach of the project is iterative and modular because the solution contains administrator, teacher, and student workflows along with backend services, database support, monitoring functions, and reporting modules. The expected outcome is a practical prototype that can help institutions manage the complete lifecycle of a lab exam more effectively, from pre-exam planning to post-exam analysis, while also serving as a foundation for future academic process automation.
