\section{Deliverables of the Project}

Project deliverables are the concrete outputs that demonstrate whether the project is progressing in a meaningful and measurable way \cite{del1}. In the context of a final year project, deliverables are not limited to the final software prototype. They also include planning artifacts, design descriptions, chapter documentation, diagrams, testing evidence, and presentation material. These deliverables help the team measure progress, align expectations with the supervisor, and ensure that the project remains grounded in documented academic work rather than ad hoc development.

For the proposed AI-Driven Lab Exam Monitoring and Management System, deliverables are especially important because the project combines practical software construction with report-based academic justification. A deliverable must therefore contribute either to system realization, project control, or academic evaluation. The following subsections explain the major deliverables in a more detailed manner.

\subsection{Requirements and Analysis Deliverables}

The first class of deliverables includes the problem analysis, literature grounding, requirement specification, workflow interpretation, and chapter documentation produced during the early stage of the project. These deliverables are important because they establish why the project is needed and what the system is expected to accomplish. They also act as a baseline against which later design and implementation decisions can be judged. If the analysis deliverables are weak, later development may become technically active but academically unfocused.

\subsection{Design Deliverables}

Design deliverables include the system model, process model illustration, work breakdown structure, scheduling diagrams, comparison tables, and any architecture-oriented descriptions used to convert requirements into a buildable plan. These outputs clarify how the system should be structured and how the development process should unfold. They reduce ambiguity by transforming general ideas into visual and textual planning artifacts. In this project, design deliverables are particularly important because the system must coordinate several interdependent modules such as scheduling, monitoring, submission management, and reporting.

\subsection{Prototype and Module Deliverables}

The major software deliverable of the project is a functional prototype of the AI-Driven Lab Exam Monitoring and Management System. However, the prototype itself is composed of smaller module-level deliverables. These include role-based login and dashboard access, exam creation and scheduling, candidate-session management, invigilator monitoring support, event logging, controlled submission handling, and report-oriented review support. Each module contributes to the completeness of the overall system, and each one must be sufficiently mature for the prototype to appear coherent rather than fragmented.

\subsection{Testing and Validation Deliverables}

Testing-related deliverables include structured validation of module behaviour, review of user flows, checking of reporting outputs, and confirmation that scheduling and monitoring logic work in a consistent manner. In an academic project, testing deliverables are essential because they show that the prototype has been examined critically rather than merely assembled. They also make it easier to explain which parts of the project were validated and which parts remain open to future improvement.

\subsection{Documentation and Presentation Deliverables}

The project report, final presentation, supervisor review responses, and supporting explanations are also critical deliverables. These outputs help communicate the purpose, structure, limitations, and contribution of the project. In many FYPs, a strong system can still be undervalued if the documentation does not explain its significance clearly. Therefore, written and presentation deliverables must be treated as central project outputs rather than end-stage formalities.

