\chapter{SOFTWARE PROJECT PLAN}
\label{chap:spp}

The Software Project Plan explains how the AI-Driven Lab Exam Monitoring and Management System will be organized, managed, tracked, and delivered throughout the final year project lifecycle \cite{spp1}. In software projects that involve multiple user roles, security-sensitive assessment workflows, real-time monitoring, evidence capture, and reporting obligations, planning is not a formality. It is the mechanism that holds the project together. Without a clear project plan, separate modules may be built in isolation, key deadlines may be missed, quality checks may become inconsistent, and documentation may fail to reflect the actual development journey.

For the proposed project, the plan is particularly important because the system integrates administrative control, invigilation support, and student-facing exam interaction within a single platform \cite{agile1}. Such integration creates dependency chains across modules. Scheduling logic affects monitoring. Monitoring affects evidence handling. Evidence handling affects reports. Reports affect post-exam academic decisions. Therefore, the project must be guided through a structured plan that balances ambition, feasibility, academic deadlines, and iterative improvement.

This chapter describes the deliverables, management approach, scheduling logic, managerial process assumptions, and risk management strategy that will guide the project. The overall aim is to ensure that development remains practical, measurable, and academically defensible from the first sprint to the final presentation.

